Gozde and Liora Replication Code

### 2015-03-09 Gozde-Liora-Replication-Code.Rmd

```{r}
library(Zelig)
library(lme4)
library(MASS)
library(nlme)
library(plm)
library(xtable)
library(foreign)
library(dplyr)
library(broom)
library(ggplot2)

data <- read.dta("nonimp.dta")
```

# Clean data and rename variables ???????

```{r}

```{r}
ggplot(data, aes(x=zsur, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) # Relationship with standardized unemployment rate

ggplot(data, aes(x=zasylumseekers, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w immigration

ggplot(data, aes(x=zreplacementrate, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w welfare (=unemp benefit)
```

@@

# Run the regression (multilevel logictic regresstion based on Quasi-penalized likelihood): All contextual variables are mean-centered (as z- connotes)

@@

```{r}
# Create vectors of coefficients, standard deviations, and variable names
coef_vec <- as.vector(model1$coef$fixed) 
N <- c(174452, 267)

sd_vec <- as.vector(sqrt(diag(model1$varFix))) #Vector of sds
var_names <- c("Male","18–29 years","30–45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers × Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")

@@

table_matrix <- cbind(coef_vec, sd_vec)

@@

rownames(table_matrix) <- c("Male","18–29 years","30–45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers × Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")

x <- xtable(table_matrix, digits = 3)
print.xtable(x, type = "html", file="tablepractice.html")

>>>>

```{r}
library(Zelig)
library(lme4)
library(MASS)
library(nlme)
library(plm)
library(xtable)
library(foreign)
library(dplyr)
library(broom)
library(ggplot2)
library(xtable)
library(stargazer)
data <- read.dta("nonimp.dta")
```

@@

```{r}
ggplot(data, aes(x=zsur, y=rexvote)) + geom_point() + geom_smooth(method = "glm", family = "binomial", se=FALSE) # Relationship w/ standardized unemployment rate

ggplot(data, aes(x=zasylumseekers, y=rexvote, color=country)) + geom_point() + geom_smooth(method= "glm", family = "binomial", se=FALSE) # Relationship w/ immigration

ggplot(data, aes(x=zreplacementrate, y=rexvote, color=country)) + geom_point() + geom_smooth(method=lm, se=FALSE) #Relationship w/ welfare (=unemp benefit)
```

# Run the regression (multilevel logictic regression based on Quasi-penalized likelihood): All contextual variables are mean-centered (as connoted by "z-")

@@

```{r}
# Create vectors of coefficients, standard deviations, and variable names

Coefficient <- as.vector(model1$coef$fixed) 
n <- c(174452, 267)

Standard_Deviation <- as.vector(sqrt(diag(model1$varFix)))

var_names <- c("Male","18–29 years","30–45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers × Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")

@@

table_matrix <- cbind(Coefficient, Standard_Deviation)

@@

rownames(table_matrix) <- c("Male","18_29 years","30_45 years",">65 years","Education: middle/high","Education: university","Petty Bourgeoisie","Worker","Pensioner","Unemployed","Left-Right","Dissatisfied: EU","Dissatisfied: Democracy","Disproportionality","Decentralization","Asylumseekers", "Unemployment", "Asylumseekers x Unemployment", "Toughness", "Salience", "Variance", "AT", "BE", "DE-E", "DE-W", "DK", "ES", "FI", "FR", "GR", "IT", "NL", "NO", "PT", "SE", "Asylumseekers x Unemployment", "Unemployment benefits x Unemployment", "Unemployment benefits x Asylumseekers", "Variance x Salience")

# Create table using xtable

x <- xtable(table_matrix, digits = 3, caption = "Logistic multilevel model. PQL2 estimates, model-based standard errors in parentheses. MI results based on 11 separate imputations.")
print.xtable(x, type = "html", file="tablepractice.html")

# Create Table 1 using stargaze

stargazer(table_matrix, title = "TABLE 1 Support for the Extreme Right: Sociodemographics, Attitudes, Country Effects, and Contextual Variables", align = TRUE, table.layout = "t", notes = "Logistic multilevel model. PQL2 estimates and model-based standard errors.", style = "ajps", out = "Table 1.html", no.space = TRUE)
